Ternary plots for `hyper2` and `hyper3` samples

### 2025-03-19 inst/fatigue.Rmd
need magrittr package
soft link for hyper2.bib

---
title: "fatigue"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

```{r setup, include=FALSE}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
library("hyper2")
```

>>>>

---
title: "fatigue"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

```{r setup, include=FALSE}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
library("hyper2")
library("magrittr")
```

### 2025-03-19 inst/retain.Rmd
bugfixes
soft link for hyper2.bib

---
title: "Keeping and discarding players: functions `keep()` and `keep_flawed()`"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

```{r}
jj <- skating_table[1:3,1:6]
rownames(jj) <- letters[1:3]
jj
```

@@

```{r}
a <- apply(jj,2,rank)
a
```

@@

```{r}
OT <- ordertable2supp(a)
OT
```

@@

```{r}
keep_flawed(OT, c("a","b"))
```

@@

```{r}
keep_flawed(OT,"a")
```

>>>>

---
title: "Keeping and discarding players: functions `keep()` and `keep_flawed()`"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

```{r subsetofskating}
jj <- unclass(skating_table)[1:3,1:6]
rownames(jj) <- letters[1:3]
jj
```

@@

```{r convexp}
a <- apply(jj,2,rank)
a
```

@@

```{r coerceto}
OT <- ordertable2supp(a)
OT
```

@@

```{r keepflaw}
keep_flawed(OT, c("a","b"))
```

@@

```{r keeponlya}
keep_flawed(OT,"a")
```

### 2025-03-19 inst/salad.Rmd
soft link for hyper2.bib

---
title: "salad"
output: bookdown::html_document2
author: "R. K. S. Hankin"
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

```{r useexplicitmethod,cache=TRUE}
H1 <- hyper2()
for(i in seq_len(nrow(salad))){
   H1 <-  H1 + ordervec2supp(as.matrix(salad)[i,])
}
H1
```

>>>>

---
title: "salad"
output: bookdown::html_document2
author: "R. K. S. Hankin"
bibliography: hyper2.bib
---

@@

```{r useexplicitmethod,cache=TRUE}
H1 <- hyper2()
for(i in seq_len(nrow(salad))){
   H1 <-  H1 + suppfun(as.matrix(salad)[i,])
}
H1
```

### 2025-03-19 inst/skeleton.Rmd
bowdlerise
soft link for hyper2.bib

---
title: "skeleton racing with the hyper2 package"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

@@

```{r,label=datamatrixfucksthingsup}
head(data.matrix(skeleton_table))
```

>>>>

---
title: "skeleton racing with the hyper2 package"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

(takes about four hours to run without cache)

@@

```{r,label=datamatrixbuggersthingsup, error=TRUE}
head(data.matrix(skeleton_table))
```

### 2025-03-19 inst/table_tennis_serve.Rmd
dirichlet3()
soft link for hyper2.bib

---
title: "The importance of serve in table tennis"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

```{r, label=newdatacd,cache=TRUE}
(Hnew <- home_away3(M_home,M_away,lambda=3.35) + pair3(c=0,d=1,lambda=3.35))
maxp(Hnew)
```

>>>>

---
title: "The importance of serve in table tennis"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

```{r, label=newdatacd,cache=TRUE}
(Hnew <- home_away3(M_home,M_away,lambda=3.35) + dirichlet3(c(c=0,d=1),lambda=3.35))
maxp(Hnew)
```

### 2025-03-19 inst/ternaryplot_hyper2.Rmd
soft link for hyper2.bib

---
title: "Ternary plots for `hyper2` and `hyper3` samples"
author: "Robin Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

>>>>

---
title: "Ternary plots for `hyper2` and `hyper3` samples"
author: "Robin Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---
